FictionEro2 - Affective Impact of Fiction

### 2025-08-01 study2/analysis/2_emotion.qmd
Update 2_emotion.qmd
cleaning script data updated

This section is about selecting the best model. Notably, **all the stimuli presented are of an erotic nature**.
Note that variables were rescaled to [0,1] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making **all stimuli relevant** to participants.

@@

::: panel-tabset

### Arousal

@@

```{r Valence plot}
estimate_relation(m_v) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Valence") +
  facet_wrap(~SexualOrientation) +
  theme_abyss()
```

:::

@@

1. Males rate AI-generated images ~0.014 lower in arousal (on average) than photos — significant.
2. Females also rate AI images lower, but not significantly.
3. Males rate couple images significantly lower in arousal than individual ones.
4. Females rate couple images significantly higher in arousal than individual ones.

m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ StimuliType/ Condition + 
                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

@@

@@

<!-- 1.For Males, giving feedback indicating that AI-generated images were less attractive, influenced arousal ratings for images labeled as AI-generated. Specifically, males who reported finding AI-generated images as less arousing had lower arousal ratings for those images.

<!-- 2. For Males, giving feedback indicating that AI-generated images were more attractive significantly influenced arousal ratings for images labeled as AI-generated. Specifically, males who reported finding AI-generated images more attractive had higher arousal ratings for these images.  -->

@@

```{r Arousal Believed}
m <- glmmTMB::glmmTMB(Arousal ~ Gender / StimuliType/Condition + (Condition|Participant) + (Condition|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

@@

@@

<!-- Note: Feedback that 'No Images were Arousing' , 'Some Images were Arousing' and the 'difference between real and photos was Subtle' only had 1 level, hence were excluded from the following analysis -->
```{r Enticement Moderator}
for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
           "BAIT_Positive", "BAIT_Negative",
           "PornFrequency", "SexualActivity")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Enticing", m))
}

@@

```{r Enticement Believed1}
m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

<!-- The intercept is Male and photograph.  -->
Women rated images overall as lower in valence than men did. They rated couple images as higher in valence than individual ones. Additionally, women rated AI-generated couple images as significantly lower in valence than photographic couple images. Men rated images of couples lower in valence and AI-images of individuals lower in valence comapred to real photos of individuals.

@@

```{r Valence Model}
m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + 
                                (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

@@

```{r Valence Believed1}
m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Emotionality Model}
m_emotionality <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

@@

```{r EMotionality Believed1}
m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

>>>>

This section is about selecting the best model. Notably, **all the stimuli presented are of an erotic nature**. Note that variables were rescaled to \[0,1\] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making **all stimuli relevant** to participants.

@@

::: panel-tabset
### Arousal

@@

```{r Valence plot}
estimate_relation(m_v) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Valence") +
  facet_wrap(~SexualOrientation) +
  theme_abyss()
```
:::

@@

1.  Males rate AI-generated images \~0.014 lower in arousal (on average) than photos — significant.
2.  Females also rate AI images lower, but not significantly.
3.  Males rate couple images significantly lower in arousal than individual ones.
4.  Females rate couple images significantly higher in arousal than individual ones.

```{r Arousal}

m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

@@

m_arousal_st <- glmmTMB::glmmTMB(Arousal ~ Gender/ StimuliType/ Condition + 
                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_arousal_st)

marginaleffects::avg_slopes(m_arousal_st, variables=c("Condition", "StimuliType"), by="Gender") |>
  results_table()
```

@@

```{=html}
<!-- 1.For Males, giving feedback indicating that AI-generated images were less attractive, influenced arousal ratings for images labeled as AI-generated. Specifically, males who reported finding AI-generated images as less arousing had lower arousal ratings for those images.

<!-- 2. For Males, giving feedback indicating that AI-generated images were more attractive significantly influenced arousal ratings for images labeled as AI-generated. Specifically, males who reported finding AI-generated images more attractive had higher arousal ratings for these images.  -->
```

@@

```{r Arousal Believed with stimuli type}
m <- glmmTMB::glmmTMB(Arousal ~ Gender / StimuliType/Condition + (Condition|Participant) + (Condition|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

```{r Arousal Believed without stimuli type}
m <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (Condition|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Enticement Model with stimuly type}
m_enticement_st <- glmmTMB::glmmTMB(Enticing ~ Gender / StimuliType/ Condition + 
                                   (Condition | Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_enticement_st)

marginaleffects::avg_slopes(m_enticement_st, variables="Condition", by="Gender") |>
  results_table()

@@

<!-- Note: Feedback that 'No Images were Arousing' , 'Some Images were Arousing' and the 'difference between real and photos was Subtle' only had 1 level, hence were excluded from the following analysis -->

```{r Enticement Moderator}
for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
           "BAIT_Positive", "BAIT_Negative",
           "PornFrequency", "SexualActivity")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Enticing", m))
}

@@

```{r Enticement Believed1 with stimuli type}
m <- glmmTMB::glmmTMB(Enticing ~ Gender/ StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

```{r Enticement Believed1 wihtout stimuli type}
m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

<!-- The intercept is Male and photograph.  -->

Women rated images overall as lower in valence than men did. They rated couple images as higher in valence than individual ones. Additionally, women rated AI-generated couple images as significantly lower in valence than photographic couple images. Men rated images of couples lower in valence and AI-images of individuals lower in valence comapred to real photos of individuals.

@@

```{r Valence Model}
m_valence <- glmmTMB::glmmTMB(Valence ~ Gender/ Condition + 
                                (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Valence Model with stimuli type}
m_valence_st <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + 
                                (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_valence_st)

marginaleffects::avg_slopes(m_valence_st, variables="Condition", by="Gender") |>
  results_table()

@@

```{r Valence Believed1 with stimuli type}
m <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

```{r Valence Believed1 without stimuli type}
m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Emotionality Model}
m_emotionality <- glmmTMB::glmmTMB(Emotionality ~ Gender/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Emotionality Model with stimuli type}
m_emotionality_st <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_emotionality_st)

marginaleffects::avg_slopes(m_emotionality_st, variables="Condition", by="Gender", re.form=NA) |>
  results_table()
```

@@

```{r EMotionality Believed1 with stimuli type}
m <- glmmTMB::glmmTMB(Emotionality ~ Gender/StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

```{r EMotionality Believed1 without stimuli type}
m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
